---
title: "Happy"
author: "Yuheng Peng"
date: "12/18/2019"
output: html_document
---

### Background Information
The studies examine the state of happiness in today’s world to demonstrate how personal and national differences in happiness are understood by the new science of happiness.



### Research Question

1.where is the most happinest countries?
2. what factors impact the happiness score.
3.Which country have greatest improve in ranking and which attribute impove the  most?




```{r}
rm(list = ls())
library(DataComputing)
library(tidyverse)
library(devtools)
library(mosaic)
```

### Data Importing
```{r}
x2018<-read.csv("D:/HW/Stat184/2018.csv")
x2019<-read.csv("D:/HW/Stat184/2019.csv")
```

### Data components

```{r}
head(x2018);
```

```{r}
head(x2019)
```



### Q1
From table 2019,the top 15 most happy countries, 10 countries from Europe, 2 countries from oceania, 1 country from Asia,1 country from North America and 1 country from Central America. From Scecond table 2018, the top 15 most happy countries, 11 countries from Europe, 2 countries from oceania,1 country from North America and 1 country from Central America.

```{r}
x2018%>%
  select(Country.or.region,Score)%>%
  arrange(desc(Score))%>%
  head(15)
```




```{r}
x2019%>%
  select(Country.or.region,Score)%>%
  arrange(desc(Score))%>%
  head(15)
```


From the world map we can see that North America have high happiniess score and Africa have low happniess score. 

```{r}
x2019%>%
WorldMap(key="Country.or.region", fill=Score)
```

## Q2

### Generosity 

```{r}
ggplot(data=x2018,aes(x=Overall.rank,y=Generosity))+
  geom_point()+
  aes(colour=Generosity) + 
  geom_smooth(method=loess)
```


```{r}
ggplot(data=x2019,aes(x=Overall.rank,y=Generosity))+
  geom_point()+
  aes(colour=Generosity) + 
  geom_smooth(method=loess) 
```








### GDP per Capital

```{r}
ggplot(data=x2018,aes(x=Overall.rank,y=GDP.per.capita))+
  geom_point()+
  aes(colour=GDP.per.capita)+
  aes(size=GDP.per.capita)+ 
  geom_smooth(method=lm) 
```





```{r}
ggplot(data=x2019,aes(x=Overall.rank,y=GDP.per.capita))+
  geom_point()+
  aes(colour=GDP.per.capita)+
  aes(size=GDP.per.capita)+ 
  geom_smooth(method=lm) 
```



### social support
```{r}
ggplot(data=x2018,aes(x=Overall.rank,y=Social.support))+
  geom_point() + 
  geom_smooth(method=lm) 
```




```{r}
ggplot(data=x2019,aes(x=Overall.rank,y=Social.support))+
  geom_point() + 
  geom_smooth(method=lm)
```






## Q3

According to the table, Benin improve the most  over past year. Benin improve 34 levels.
```{r}
x2019%>%
  mutate(rank19=Overall.rank,Country=Country.or.region)%>%
  select(Country,rank19)%>%
  left_join(x2018%>%
          select(Country.or.region,Overall.rank),by=c("Country"="Country.or.region"))%>%
  mutate(improveRank=Overall.rank-rank19)%>%
  arrange(desc(improveRank))

```




```{r}
#mutate data
HP2019<- x2018%>%
  mutate(Country=Country.or.region,GDP1=GDP.per.capita,SS1=Social.support,HL1=Healthy.life.expectancy,FREE1=Freedom.to.make.life.choices,GE1=Generosity,POF1=Perceptions.of.corruption)%>%
  filter(Country=="Benin")%>%
  select(Country,GDP1,SS1,HL1,FREE1,GE1,POF1)

HP2018<- x2019%>%
  mutate(Country=Country.or.region,GDP2=GDP.per.capita,SS2=Social.support,HL2=Healthy.life.expectancy,FREE2=Freedom.to.make.life.choices,GE2=Generosity,POF2=Perceptions.of.corruption)%>%
    filter(Country.or.region=="Benin")%>%
  select(Country,GDP2,SS2,HL2,FREE2,GE2,POF2)
```



### What is changed in Benin

According to the calculation, Benin’s 5 attributes GDP per capita, social support, Healthy life expectancy, Generosity and corruption increase easpecially the Healthy life expectancy， it grows 65% in 2018 and that makes Benin’s happiniess score higher and improve it’s rank from 136 to 102


```{r}
HP2019
```



```{r}
HP2018
```


```{r}
#define function
calculate=function(x,y){
  improve=(x-y)/y
  improve=improve*100
  return(improve)
}

```


```{r}
#calculate GDP
calculate(0.393,0.378)
```



```{r}
#calculate Health
calculate(0.397,0.24)
```



```{r}
#calculate Generosity
calculate(0.175,0.163)
```


```{r}
#calculate corruption
calculate（0.082，0.067)
```


```{r}
#calculate Free choice
calculate(0.349,0.44)
```




















































